An Adolescent Mini-Neptune in the Kepler Field

### 2021-08-13 paper/ms.tex
update RM model comparison

The final line of evidence confirming \pn\ comes from a spectroscopic
transit we measured from Keck/HIRES during the night of 7 Aug 2021
(UT), using the iodine cell for the wavelength calibration.  We
scheduled the transit using the ephemeris of
\citet{holczer_transit_2016}, which we verified using the available
TESS data.  We also acquired simultaneous multi-band photometry using
MUSCAT3, to help interpret the radial velocities \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The spectroscopic data show significant scatter, though a significant
increase in radial velocity is seen shortly after the expected
ingress.  We fitted the RVs using the \citet{hirano_analytic_2010} and
\citet{hirano_2011} models for the Rossiter-McLaughlin effect, and
considered the cases of a linear and quadratic trend.
% TODO finish this paragraph
We found $\chi^2_{\rm red} = X.XX$ for the best-fitting linear case, 
and
$\chi^2_{\rm red} = X.XX$ for the best-fitting quadratic, with a
$\Delta {\rm BIC} = Y.YY$ between the two, providing {\bf (very)
strong} evidence to prefer the latter.

>>>>

% from /drivers/logs/rm.log
% quad: 
% chi2red 4.45
% BIC 272.4
%
% linear:
% chi2red 17.1
% BIC 291.8
%
% trendonly:
% chi2red 13.8
% BIC 271.3

The final line of evidence confirming \pn\ comes from a spectroscopic
transit we measured from Keck/HIRES during the night of 7 Aug 2021
(UT), using the iodine cell for the wavelength calibration.  We
scheduled the transit using the ephemeris of
\citet{holczer_transit_2016}, which we verified using the available
TESS data.  We also acquired simultaneous multi-band photometry using
MUSCAT3, to help interpret the radial velocities \citep{Narita_2020}.
The lower panels in Figure~\ref{fig:obliquity} show the results.  The
photometry shows the expected starspot trend, along with the transit
and a likely starspot crossing event at ${\rm JD} - 2459433 = 0.955$.
The radial velocities show significant scatter, though a significant
increase in RV is seen shortly after the expected ingress.  The
internal uncertainties on the RVs ($\approx 15\,{\rm m\,s}^{-1}$)is
dominated by the $v\sin i$ broadening.

We fitted the RVs using the \citet{hirano_analytic_2010,hirano_2011}
models for the Rossiter-McLaughlin (RM) effect, and allowed for a
linear and optionally quadratic trend, along with a white-noise jitter
term.  We found $\chi^2_{\rm red} = 17.1$ for the best-fitting linear
case, and $\chi^2_{\rm red} = 16.7$ for the best-fitting quadratic,
with a $\Delta {\rm BIC} = {\rm BIC}_{\rm lin} - {\rm BIC}_{\rm quad}
= 19.3$.  Nominally, this provides strong statistical evidence to
prefer the quadratic model over the linear one.  However the
$\chi^2_{\rm red}$ indicate that neither fit is particularly good.
Considering a quadratic trend alone without any RM effect yields
$\chi^2_{\rm red} = 13.8$, and $\Delta {\rm BIC} = {\rm BIC}_{\rm
trend} - {\rm BIC}_{\rm quad} = 1.2$; from a model-comparison
standpoint, there is no statistical justification to prefer the
best-fitting ``RM + quadratic trend'' model over the best-fitting
``quadratic trend'' model, or vice-versa.  Given the expected
semi-amplitude of the velocity anomaly ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$) and the achieved internal precision, the claim
of having ``detected the Doppler transit'' is perhaps not yet
justified.  Observationally however, we know from the MUSCAT3 data
that the transit was observed, and the increase in radial velocity
seen shortly after ingress also seems consistent with a prograde or
polar orbit, and not a retrograde one.  More precise data will likely
be required to make a more precise measurement of the obliquity.
